---
title: "Analysis of the LifeSpans dataset"
author: "Camden Heafitz"
date: "2023-10-27"
date-format: iso
format: pdf
editor: source
---

```{r}
#| label: setup
#| include: false
library(mosaic)   
library(tidyverse)
# instructions to install the package
# devtools::install_github("STAT231-F23/DiscGolf")
library(LifeSpans)
```

This file provides an overview of the LifeSpans package as well as some sample analyses.

The `LifeSpans` package containes sex-specific sample sizes and mean life expectancies of 
zoo animal species in North American zoos as of January, 2019. Association as of October, 2020.
This package may be of interest to those who study animals or perhaps become a veterinarian. 

```{r}
#| label: fig-myfigure
#| fig.cap: "XX MY CAPTION"
#| warning: false
#| fig.width: 6
#| fig.height: 8
LifeSpans |>
  mutate(
    weight_grp = cut_number(
      weight, 
      3,
      labels = c("<175gm", "175-177gm", "177+gm")
    )
  ) |>
  ggplot(aes(x = approved_date, y = flexibility, color = weight_grp)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  labs(x = "Date of approval", y = "Flexibility (in kg)", color = "Weight group") +
  theme(legend.position = "top")
```

We see in @fig-myfigure that XX add interpretation here XX.
