---
title: "Analysis of the LifeSpans dataset"
author: "Camden Heafitz"
date: "2023-10-27"
date-format: iso
format: pdf
editor: source
---

```{r}
#| label: setup
#| include: false
library(mosaic)   
library(tidyverse)
# instructions to install the package
# devtools::install_github("STAT231-F23/LifeSpans")
library(LifeSpans)
```

This file provides an overview of the LifeSpans package as well as some sample analyses.

The `LifeSpans` package contains sex-specific sample sizes and the mean life expectancy of 
zoo animal species in North American zoos as of January, 2019. This package may be of interest to those who study animals or perhaps become a veterinarian. 

```{r}
#| label: fig-myfigure
#| fig.cap: "XX MY CAPTION"
#| warning: false
#| fig.width: 6
#| fig.height: 8
LifeSpans |>
  group_by(taxon)|>
  ggplot(aes(x = malemle, y = femalemle, color = taxon)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  labs(x = "Male Mean Life Expectancy", y = "Female Mean Life Expectancy", color = "Taxonomic Class") +
  theme(legend.position = "top")
```

We see in @fig-myfigure that XX add interpretation here XX.
